Supplementary Materials

### 2018-03-27 paper/appendix_modelDescription.tex
add legend for optimized

\section{Appendix B: Code Example: Link Visualization with Model}
\begin{lstlisting}[language=Python, caption=Code for generating the visualization.]
from visPackage import *
from modelInterface import *
from sentenceGenerator import *

@@

#setup model callbacks
vis.setPredictionHook(model.predict)
vis.setAttentionHook(model.attention)
vis.setPredictionUpdateHook(model.updatePrediction)
vis.setAttentionUpdateHook(model.updateAttention)
vis.setReloadModelCallback(model.reloadModel)
vis.setPipelineStatisticHook(model.pipelineStatistic)

>>>>

\section{Appendix B: Code Example: Link Visualization with Model}
From the user point of view, the following python script is all the code the domain expert needs to link the NLP model with the visual interface. The visualization library's API defines several callbacks (call Hook in the code) that describe the model functionality (e.g., prediction) need to supplied by the NLP model.

\begin{lstlisting}[language=Python, caption=Code for generating the visualization.]
from visPackage import *
from modelInterface import *
from sentenceGenerator import *

@@

#setup model callbacks
vis.setPredictionHook(model.predict)
vis.setAttentionHook(model.attention)
vis.setPredictionUpdateHook(model.updatePrediction)
vis.setAttentionUpdateHook(model.updateAttention)
vis.setReloadModelHook(model.reloadModel)
vis.setPipelineStatisticHook(model.pipelineStatistic)

### 2018-03-27 paper/application.tex
add legend for optimized

\section{Application Scenarios}
\label{sec:caseStudy}
% \shusen{A full case study that driven by the visualization task and the question associated with them}
In this section, we discuss application scenarios, in which the domain experts utilize the perturbation driven analysis to explore and assess the model and interpret the attention mechanism.
%
These scenarios are summarized by the domain experts who integrated the tool into their model exploration workflow.

\subsection{Scenario 1: Interpretting Model Decision Making Process}
The three stages (encoder, attention, classifier) of the model work in synergy to produce the correct prediction.
% \shusen{difference in sensitivity among entail natural and contradict relationships}
% the generate the correct prediction for the wrong reason

\subsection{Scenario 2: Which Part of the Model is the Problem?}

\subsection{Scenario 3: Handcraft Example Exploration}
Well-know tough examples, such as the Facebook IPO example discussed in Section~\ref{sec:background}.

\subsection{Scenario 4: Handcraft Example Exploration?}

%\subsection{Is the Prediction Stable?}
%\subsection{Where Are the Mistakes?}
%\subsection{How Attention Affect the Prediction?}
%\subsection{What Does It Take to Change the Prediction?}
%\subsection{Is Attention All You Need?}

>>>>

\section{Application Scenarios}
\label{sec:caseStudy}
% \shusen{A full case study that driven by the visualization task and the question associated with them}
In this section, we discuss application scenarios, in which the domain experts utilize the perturbation driven analysis to explore and assess the model and interpret the attention mechanism.
These scenarios are summarized by the domain experts who try to integrate the tool into their workflow.

\subsection{Scenario 1: Interpreting Decision Making Process}
The three stages (encoder, attention, classifier) of the model work in synergy to produce the correct prediction.
%
Mistake can be made in either of these stages.
% \shusen{difference in sensitivity among entail natural and contradict relationships}
% the generate the correct prediction for the wrong reason

\subsection{Scenario 2: Assess the Model Prediction Stability}
Utilize input sentence perturbation to assess the overall stability of the prediction

\subsection{Scenario 3: What Does It Take to Correct the Prediction?}
In the previous section, we discussed how we can use forward prediction

\subsection{Scenario 4: Handcraft Example Analysis}
Well-known tough examples, such as the Facebook IPO example discussed in Section~\ref{sec:background}.

\subsection{Scenario 5: Grammar Structure and Attention}
Can attention capture grammar structure? Is 
%\subsection{Is the Prediction Stable?}
%\subsection{Where Are the Mistakes?}
%\subsection{How Attention Affect the Prediction?}
%\subsection{What Does It Take to Change the Prediction?}
%\subsection{Is Attention All You Need?}
